Manuscript Figures

### 2021-09-16 src/manuscript_figures.Rmd
move partition comparison supp-figure to the end
update tmz+gbm analysis to include umap and survival plots

# cross-validation results predicting TMZ resistance using 
# maui LFs and other known markers 
aucs <- data.table::fread(file.path(folder, 'aucs.csv'))
aucs$group <- ifelse(grepl('LF', aucs$method), 'maui', 'no-maui')
aucs$method <- gsub("LF[Ss]", "MAUI LFs", aucs$method)
colnames(aucs)[2] <- c('AUC')
Fig <- ggpubr::ggbarplot(aucs, x = 'method', y = 'AUC', add = 'mean_se',
                  fill = 'group') +
  theme(axis.title.x = element_blank(), legend.position = 'none', 
        ) + 
  scale_fill_brewer(type = 'qual', palette = 3)

>>>>

# cross-validation results predicting TMZ resistance using 
# maui LFs and other known markers 
aucs <- data.table::fread(file.path(folder, 'aucs.csv'))
aucs$group <- ifelse(grepl('LF', aucs$method), 'maui', 'no-maui')
aucs$method <- gsub("LF[Ss]", "MAUI LFs", aucs$method)
colnames(aucs)[2] <- c('AUC')

p1 <- ggpubr::ggbarplot(aucs, x = "method", y = 'AUC', add = 'mean_se',
                  fill = 'group') +
  coord_flip() + 
  theme(axis.title.y = element_blank(), legend.position = 'none') + 
  scale_fill_brewer(type = 'qual', palette = 3)

# umap responders
umap <- data.table::fread(file.path(folder, 'umap_coords_and_response.csv'))
colnames(umap)[2:3] <- c('UMAP1', 'UMAP2')
#drop samples without umap coords
umap <- umap[!is.na(UMAP1)][!is.na(UMAP2)]
umap$response <- ifelse(umap$response == TRUE, 'responder', 'non-responder')
umap[is.na(response)]$response <- 'unavailable'
umap[is.na(response)]$color <- 'gray'
p2 <- ggscatter(umap, x = 'UMAP1', y = 'UMAP2', color = 'response', size = 2)  + 
  scale_color_manual(values = c('dodgerblue', 'firebrick', 'gray')) + 
  theme(legend.title = element_blank())

# survival plots
gbm_surv <- read.csv(file.path(folder, "survival_time_response_and_predictions.csv"), row.names = 1)
gbm_surv <- gbm_surv[,c(3, 5:7)]
panel_titles <- c('observed response', 'MAUI + MGMT', 
                  'MAUI + MGMT-expression', 'MAUI + MGMT-methylation')
plots <- sapply(simplify = F, 1:ncol(gbm_surv), function(i) {
  x <- colnames(gbm_surv)[i]
  plot_survival(surv, partition.df = gbm_surv[,x,drop = F], duration_col = 'PFI.time', event_col = 'PFI')[['plot']] + 
    ggtitle(label = panel_titles[i]) + theme(legend.direction = 'vertical', legend.title = element_blank(), 
                                             legend.position = c(0.5, 0.8))
})

Fig <- cowplot::plot_grid(cowplot::plot_grid(p1, p2, labels = c('A', 'B')),
                          cowplot::plot_grid(plotlist = plots, ncol = 2, labels = c('C', 'D', 'E', 'F')), 
                          nrow = 2, rel_heights = c(1.5, 2))
